E1: ENRON Sentiment

### 2016-03-25 paper/paper.tex
uo

\section{Experiments}
\label{sec:exp}
In this section we briefly explain the experiments run in order to obtain our results.
\hlc{TODO THIS!!!!!!!!!!!}

>>>>

\section{Experiment}
\label{sec:exp}
In this section we briefly explain the experiment run in order to obtain our results.
After running the setup described in Section~\ref{sec:p-s}, we collect the output data.
Then, we perform a post processing step in which we firstly resample the time series on a weekly (i.e., 7 days) basis using the average as aggregation function.
Moreover, we apply an interpolation function (i.e., polynomial, $4^{th}$ order) to smooth out our time series.
The result is shown in Figure~\ref{fig:sentiment_vs_stock}.

\begin{figure}[h!]
\centering
\includegraphics[width=0.48\textwidth]{imgs/sentiment_vs_stock}
\caption{Time series of ENRON's stock price (blue) and sentiment values extracted from emails (green), from 2000-01-01 to 2001-12-31.}
\label{fig:sentiment_vs_stock}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=0.48\textwidth]{imgs/sentiment_dist_hist}
\caption{Distribution of sentiment values extracted from emails, from 2000-01-01 to 2001-12-31.}
\label{fig:sentiment_dist_hist}
\end{figure}
